Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-10-01 Manuscript/Manuscript.Rmd
working on intro

bibliography      : ["HarpNetaInPrep.bib"]

@@

### load necessary libraries ###
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(broom))
```
# Introduction
## Working memory and load theory
Despite extensive research on the interaction of working memory and affective processes, there is still debate in the literature concerning how this cognitive process and emotional processes affect one another. Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues -[@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli. This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility. Other work has focused on the effects of moods or affective states on working memory performance. For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2012]. Similarly, working memory processes may alter concurrent affective processes. For instance, actively engaging working memory can mitigate emotional responses. Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@dillen_tuning_2008]. Additionally, depending on one's levels of trait-rumination, low trait-ruminators are better able to return heart rate and blood pressure to baseline levels when provided with a distractor task following an anger induction [@gerin_role_2006]. Together, these studies suggest a resource competition between cognitive and emotional processing; that is, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.

While previous work clearly suggests an inhibitory role for cognitive demands on emotional responses, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli. For instance, Schmeichel and colleagues -[@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral and negative sitmuli [@dillen_tuning_2008], or even reducing symptoms of disorders with affective symptoms, such as anxiety [@spangler_little_2017]. However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the types of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies). For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food would be (in)congruent with one's current goals. This emotional appraisal is completed under concurrent laod demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state. If maintaining a goal state or some stimulus in working memory results in a large cognitive (not perceptual) load, then  Lavie's -[@lavie_load_2004] load theory posits that less executive resources are available to regulate incoming perceptual information. In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads.

Emotional stimuli readily capture attention compared to neutral stimuli, even in participants with amygdala damage [@hodsol_attentional_2011; @piech_attentional_2011]. Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals. Indeed, negative emotional content slows performance on an n-back task [@kensinger_effect_2003]. Other domain-specific effects have been observed in many lines of research, including those beyond the working memory domain. For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008]. Given the behavioral and neurological evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments.

@@

## The contribution of valence bias
<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> As mentioned above, individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item, as either positive or negative. <!-- Additionally, facial expressions can serve as ambiguously valenced stimuli. While most facial expressions send a clear social signal, this is not always the case. While a smile likely expresses a positive affective state, other cues are not so clear.--> This tendency is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes (or items) to quantify this individual difference (CITE). Biases towards negativity are related to psychopathology, such as depression and anxiety [@matthews_cognitive_2005]

@@

Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes. For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016]. Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010]. Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well. For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018]. <!-- Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. THIS NEEDS TO BE REWORKED --> In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.

Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference. Mattek and colleagues [-@mattek_differential_2016] recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories. While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias. Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.

## The present study
In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains. We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials. Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.

<!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive. -->

Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces [@mattek_differential_2016; @neta_dont_2016]. 
The valence bias is trait-like [@neta_corrugator_2009] and generalizes to non-face stimuli [@neta_neural_2013]; however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding [@brown_cortisol_2017; @neta_dont_2016]. Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology [@petro_initial_2018], at least in children. Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety [@matthews_cognitive_2005].

<!-- Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite]. Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001]. This effect holds up in the emotional domain; for example, the Stroop task [@stroop_studies_1935] has been modified by some researchers to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008]. -->

<!-- Notes: Allie showed that depletion doesn't affect ratings, but we thought that there may be an effect of specific domains of depletion (i.e., neutral vs. emotional) on ratings. Focus on EMO > NEU ratings and POS > NEG MDs. MT analyses could be supplementary material, but you'll be going down the rabbit hole.  -->
<!-- Recently, others have suggested a dynamic social trait space model for judgments of faces [@stolier_dynamic_2018], and it may be important to consider additional components of the categorization process, such as domain-specific loads.  -->

# Methods
## Participants
``` {r read data}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-09-06_12-18-56.csv")
```
Fifty-eight subjects were recruited from the undergraduate research pool at the University of Nebraska-Lincoln. The data from eight subjects were excluded due to technical difficulties resulting from an error in one of the experiment scripts. This left 50 individuals in the final sample for analysis. The mean age of the remaining sample was `r printnum(mean(data$age))` (`r printnum(sd(data$age))`), a majority of participants were female (`r printnum((sum(data$sex == "Female") / nrow(data))*100)`%), and all were white/caucasian without hispanic/Latinx ethnicity. All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the University of Nebraska-Lincoln Institutional Review Board (Approval #20141014670EP). Each participant received course credit for completing the study.

@@

# aov.data <- friedman.data
# aov.data$load <- recode(aov.data$Condition, "lo.neu.sur_rate" = "low",
#                         "hi.neu.sur_rate"= "high",
#                         "lo.emo.sur_rate"= "low",
#                         "hi.emo.sur_rate"= "high")
# aov.data$type <- recode(aov.data$Condition, "lo.neu.sur_rate" = "neu",
#                         "hi.neu.sur_rate"= "neu",
#                         "lo.emo.sur_rate"= "emo",
#                         "hi.emo.sur_rate"= "emo")
# summary(aov(`Percent Negative Ratings` ~ load * type, data = aov.data))
```
Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's < .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different rank-order distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content, and this was true for both low and high loads. Low emotional load ratings were significantly more negative than low, Z = `r (printnum(lo.emo.v.lo.neu$z_val))`, p = `r (printp(lo.emo.v.lo.neu$p.value))`, neutral and high, Z = `r (printnum(lo.emo.v.hi.neu$z_val))`, p `r (printp(lo.emo.v.hi.neu$p.value))`, neutral loads. The same was true for high emotional load ratings and low, Z = `r (printnum(hi.emo.v.lo.neu$z_val))`, p `r (printp(hi.emo.v.lo.neu$p.value))`, and high, Z = `r (printnum(hi.emo.v.hi.neu$z_val))`, p `r (printp(hi.emo.v.hi.neu$p.value))`, neutral loads. However, there was no effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = `r (printnum(lo.emo.v.hi.emo$z_val))`, p = `r (printp(lo.emo.v.hi.emo$p.value))`, and neutral, Z = `r (printnum(lo.neu.v.hi.neu$z_val))`, p = `r (printp(lo.neu.v.hi.neu$p.value))`, load ratings were not significantly different [^2]. 
<!-- double check that this is true for the repeated measures ANOVA analysis too -->
``` {r plot figure 1, include = TRUE}
friedman.data$Condition <- factor(friedman.data$Condition, levels = c("lo.emo.sur_rate", "hi.emo.sur_rate",
                                                                      "lo.neu.sur_rate", "hi.neu.sur_rate"))
friedman.data$Condition <- recode(friedman.data$Condition, "lo.emo.sur_rate" = "Low Emotional", "hi.emo.sur_rate" = "High Emotional",
                                                            "lo.neu.sur_rate" = "Low Neutral", "hi.neu.sur_rate" = "High Neutral")
friedman.data$`Percent Negative Ratings` <- friedman.data$`Percent Negative Ratings` * 100
ggplot(friedman.data, aes(Condition, `Percent Negative Ratings`, fill = Condition)) +
  geom_bar(stat = "summary", fun.y = "mean") +
  scale_fill_manual(values = c("#0d7378", "#21e1eb", "#498526", "#65e01d")) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1) +
  expand_limits(y=c(0, 100)) +
  theme(axis.text.x=element_blank()) +
  theme_apa()

>>>>

bibliography      : ["CANLab_UNL.bib"]

@@

### load necessary libraries ###
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(broom))
```
# Introduction
## Working memory and load theory
Despite extensive research on the interaction of working memory and affective processes, there is much to learn concerning how cognitive and emotional processes affect one another. Executive functions, including working memory, are related to successful self-regulation, and in turn emotion regulation [@hofmann_executive_2012]. Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues [-@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli. This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility. Other work has focused on the effects of moods or affective states on working memory performance. For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2013]. Similarly, active working memory processes may alter concurrent affective processes. For instance, actively engaging working memory can mitigate emotional responses, particularly to negative stimuli. Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@van_dillen_tuning_2009]. Additionally, following an anger induction, those with low trait rumination show faster blood pressure recovery when provided with a distractor task [@gerin_role_2006]. Together, these studies suggest a resource competition between cognitive and emotional processes; in other words, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.

While previous work suggests an inhibitory effect on some emotional responses during periods with high cognitive demands, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli. For instance, Schmeichel and colleagues [-@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral compared to negative sitmuli [@van_dillen_tuning_2009].<!--  Others have even measured symptoms during working memory maintenance of affective symptoms (i.e., typically increased negative affect), such as anxiety [@spangler_little_2017].--> However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the images of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies). For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food is (in)congruent with one's current goals. This emotional appraisal is completed under concurrent load demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state. Maintenance of one's goal state, such as a diet, can reduce performance on some components of executive functioning tasks [@shaw_dieting_2004]. These observations are in line with Lavie and colleague's [-@lavie_load_2004] load theory, which posits that under a large cognitive load less executive resources are available to regulate incoming stimulus information. <!-- In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads. -->

Recently, cognitive load theory researchers have tested, and demonstrated, the domain-specificity of load and distractor interference in visual, spatial, and phonological domains [@burnham_components_2014]. Load interference effects may also transverse other domain componenets, such as emotional compared to neutral memory content. Emotional stimuli readily capture attention compared to neutral stimuli, and this is true even in participants with amygdala damage [@hodsoll_attentional_2011; @piech_attentional_2011]. Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals. Indeed, Kensigner and colleagues [-@kensinger_effect_2003] showed that negative emotional content slows performance on the n-back task. Other domain-specific effects have been observed in many lines of executive functions research, including those beyond the working memory domain. For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Other neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008]. Given this evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent interpretations of emotional stimuli with ambiguous valence.

@@

## Interpreting ambiguity
<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> Individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item or a surprised facial expression, as either positive or negative. <!-- Additionally, facial expressions can serve as ambiguously valenced stimuli. While most facial expressions send a clear social signal, this is not always the case. While a smile likely expresses a positive affective state, other cues are not so clear.--> This is attributable to these stimuli's predictive value for both positive and negative outcomes. For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events. This affective bias is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes to quantify this individual difference [@neta_corrugator_2009; @neta_primacy_2010; @neta_neural_2013]. Chronic negativity biases in memory and attention are related to psychopathology, such as depression and anxiety [@mathews_cognitive_2005], suggesting the importance of understanding the factors that contribute to individuals' biases. Importantly, the valence bias is a stable measure with participants showing positively correlated scores across a one year time gap [@neta_corrugator_2009]. Despite the relative stability of the measure, experimental manipulations are capable of shifting an individuals bias [@brown_cortisol_2017; @neta_through_2018; @neta_its_2018].

Myriad factors contribute to an individual's bias, but the initial interpretation is thought to be negative across individuals. Data supporting this initial negativity hypothesis come from many studies. For instance, reaction times are faster for negative interpretations of ambiguous stimuli [@neta_dont_2016]. Additionally, presentation of surprised facial expressions as low spatial frequency images, which are processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010]. Under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes, and there is evidence to support this as well. For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Evidence from the neuroimaging literature supports the initial negativity hypothesis as well; more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018]. Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation on the mouth is related to more positive interpretations of surprised faces [@neta_all_2017].  Further, forcing gaze patterns to match those of the participants with the most negative or positive bias modulated interpretations of surprised expressions [@neta_through_2018]. In all, valence bias is a useful metric for understanding both trait-like components of individuals' affective biases, as well as gauging the effects of other experimental maniuplations on affective biases. 

@@

<!-- Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes. For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016]. Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010]. Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well. For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018]. <!-- Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. THIS NEEDS TO BE REWORKED In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.  -->

Given the evidence that a regulatory mechanism is necessary for positive interpretations of ambiguity, a demanding cognitive load might interfere with successful regulation. Indeed, Mattek and colleagues [-@mattek_differential_2016] recently showed that high levels of cognitive load (i.e., holding either a single or seven digit number in working memory) mitigates mouse trajectory deviations to the modal response. However, there was no effect on subjective valence interpretations. Just as phonological and visual cognitive loads and distractors showed domain-specificity [@burnham_components_2014], and that domain-speicificity is observed in BOLD data [@egner_dissociable_2008], a domain-specific cognitive load may differentially affect interpretations of ambiguity. In other words, there is likely a relationship between the qualities of stimuli held in working memory and effects on concurrent task processing. Here, we aim to test the effects of low and high working memory loads in both emotional and neutral domains on valence bias. We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials, as the high cognitive demand interferes with the regulatory mechanisms used to arrive at a positive interpretation. Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.

<!-- domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference. Mattek and colleagues [-@mattek_differential_2016]  While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias. Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed. -->
<!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive. -->
<!-- Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite]. Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001]. This effect holds up in the emotional domain; for example, the Stroop task [@stroop_studies_1935] has been modified by some researchers to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008]. -->
<!-- Notes: Allie showed that depletion doesn't affect ratings, but we thought that there may be an effect of specific domains of depletion (i.e., neutral vs. emotional) on ratings. Focus on EMO > NEU ratings and POS > NEG MDs. MT analyses could be supplementary material, but you'll be going down the rabbit hole.  -->
<!-- Recently, others have suggested a dynamic social trait space model for judgments of faces [@stolier_dynamic_2018], and it may be important to consider additional components of the categorization process, such as domain-specific loads.  -->
# Methods
## Participants
``` {r read data}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-09-06_12-18-56.csv")
```
Fifty-eight subjects were recruited from the undergraduate research pool at the University of Nebraska-Lincoln. The data from eight subjects were excluded due to technical difficulties resulting from an error in one of the experiment scripts. This left 50 individuals in the final sample for analysis. The mean age of the remaining sample was `r printnum(mean(data$age))` (`r printnum(sd(data$age))`), a majority of participants were female (`r printnum((sum(data$sex == "Female") / nrow(data))*100)`%), and all were white/caucasian without hispanic/Latinx ethnicity. All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the University of Nebraska-Lincoln Institutional Review Board (Approval #20141014670EP). Each participant received course credit for completing the study.

@@

# aov.data <- friedman.data
# aov.data$load <- recode(aov.data$Condition, "lo.neu.sur_rate" = "low",
#                         "hi.neu.sur_rate"= "high",
#                         "lo.emo.sur_rate"= "low",
#                         "hi.emo.sur_rate"= "high")
# aov.data$type <- recode(aov.data$Condition, "lo.neu.sur_rate" = "neu",
#                         "hi.neu.sur_rate"= "neu",
#                         "lo.emo.sur_rate"= "emo",
#                         "hi.emo.sur_rate"= "emo")
# summary(aov(`Percent Negative Ratings` ~ load * type, data = aov.data))
```
Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's < .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different rank-order distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content, and this was true for both low and high loads. Low emotional load ratings were significantly more negative than low, Z = `r (printnum(lo.emo.v.lo.neu$z_val))`, p = `r (printp(lo.emo.v.lo.neu$p.value))`, neutral and high, Z = `r (printnum(lo.emo.v.hi.neu$z_val))`, p `r (printp(lo.emo.v.hi.neu$p.value))`, neutral loads. The same was true for high emotional load ratings and low, Z = `r (printnum(hi.emo.v.lo.neu$z_val))`, p `r (printp(hi.emo.v.lo.neu$p.value))`, and high, Z = `r (printnum(hi.emo.v.hi.neu$z_val))`, p `r (printp(hi.emo.v.hi.neu$p.value))`, neutral loads. However, there was no effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = `r (printnum(lo.emo.v.hi.emo$z_val))`, p = `r (printp(lo.emo.v.hi.emo$p.value))`, and neutral, Z = `r (printnum(lo.neu.v.hi.neu$z_val))`, p = `r (printp(lo.neu.v.hi.neu$p.value))`, load ratings were not significantly different [^2]. 
<!-- double check that this is true for the repeated measures ANOVA analysis too -->
``` {r plot figure 1, include = TRUE}
friedman.data$Condition <- factor(friedman.data$Condition, levels = c("lo.emo.sur_rate", "hi.emo.sur_rate",
                                                                      "lo.neu.sur_rate", "hi.neu.sur_rate"))
friedman.data$Condition <- recode(friedman.data$Condition, "lo.emo.sur_rate" = "Low Emotional", "hi.emo.sur_rate" = "High Emotional",
                                                            "lo.neu.sur_rate" = "Low Neutral", "hi.neu.sur_rate" = "High Neutral")
friedman.data$`Percent Negative Ratings` <- friedman.data$`Percent Negative Ratings` * 100
ggplot(friedman.data, aes(Condition, `Percent Negative Ratings`, fill = Condition)) +
  geom_bar(stat = "summary", fun.y = "mean") +
  scale_fill_manual(values = c("#0d7378", "#21e1eb", "#498526", "#65e01d")) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1) +
  expand_limits(y=c(0, 100)) +
  theme_apa() +
  theme(axis.text.x=element_blank())
